```{r, results="asis", echo=FALSE}
knitr::opts_chunk$set(error=FALSE)
if (!exists(".version")) {
    .version <- package_version("1.0")
}
```

```{r, results="asis", echo=FALSE}
cat("# Binary comparison (", as.character(.version), ")", sep="")
```

## Overview

A binary comparison operation involves an element-wise comparison between two delayed objects of the same shape.

## Specification

A binary comparison operation is represented as a HDF5 group with the following attributes:

- `delayed_type` should be a scalar string `"operation"`.
  Any HDF5 string datatype may be used here.
- `delayed_operation` should be a scalar string `"binary comparison"`.
  Any HDF5 string datatype may be used here.

Inside the group, we expect:

- A `left` group, containing a delayed object on the left of the comparison operation.
  If `right` contains strings, so should `left`; otherwise, `left` can any of boolean, integer or float.
- A `right` group, containing a delayed object on the right of the operation.
  This should have exactly the same dimensions as the `left` object.
  If `left` contains strings, so should `right`; otherwise, `right` can be any of boolean, integer or float.
- A `method` string scalar dataset, specifying the comparison method to use.
  This can be any one of `==`, `<`, `>`, `>=`, `<=`, or `!=`. 
  Any HDF5 string datatype may be used here.

The type of the output object is always boolean.
For non-string `left` and `right` that are of different types, the less advanced type is promoted to a more advanced type prior to comparison.
