```{r, results="asis", echo=FALSE}
knitr::opts_chunk$set(error=FALSE)
if (!exists(".version")) {
    .version <- package_version("1.0")
}
```

```{r, results="asis", echo=FALSE}
cat("# Binary arithmetic (", as.character(.version), ")", sep="")
```

## Overview

A binary arithmetic operation involves applying an element-wise arithmetic operation on two delayed objects of the same shape.

## Specification

A binary arithmetic operation is represented as a HDF5 group with the following attributes:

- `delayed_type` should be a scalar string dataset, of any datatype that can be represented by a UTF-8 encoded string.
  It should contain the value `"operation"`.
- `delayed_operation` should be a scalar string dataset, of any datatype that can be represented by a UTF-8 encoded string.
  It should contain the value `"binary arithmetic"`.

Inside the group, we expect:

- A `left` group, containing a delayed object on the left of the arithmetic operation.
  This can be either boolean, integer or float.
  Booleans are promoted to integers for the purpose of this operation.
- A `right` group, containing a delayed object on the right of the operation.
  This can be either boolean, integer or float.
  Booleans are promoted to integers for the purpose of this operation.
  The `right` object should have exactly the same dimensions as the `left` object.
- A `method` string scalar dataset, specifying the arithmetic method to use.
  This can be any one of `+`, `-`, `/`, `*`, `^`, `%%` (modulo) or `%/%` (integer division).
  The datatype of the dataset should be representable by a UTF-8 encoded string.

The type of the output object depends on the operation, the type of `left` and the type of `right`:

- For simple division, the output type is always float.
- For integer division, the output type is always integer.
- For all other operations:
  - If the types of `left` and `right` are the same, the output of the arithmetic operation is equal to that type.
  - Otherwise, the less advanced type is promoted to a more advanced type, and the output of the arithmetic operation is equal to the promoted type.

Note that no guarantees are provided with respect to the over/underflow of the output type.
