```{r, results="asis", echo=FALSE}
knitr::opts_chunk$set(error=FALSE)
if (!exists(".version")) {
    .version <- package_version("1.0")
}
```

```{r, results="asis", echo=FALSE}
cat("# Binary arithmetic (", as.character(.version), ")", sep="")
```

## Overview

A binary arithmetic operation involves applying an element-wise arithmetic operation on two delayed objects of the same shape.

## Specification

A binary arithmetic operation is represented as a HDF5 group with the following attributes:

- `delayed_type` should be a scalar string `"operation"`.
  Any HDF5 string datatype may be used here.
- `delayed_operation` should be a scalar string `"binary arithmetic"`.
  Any HDF5 string datatype may be used here.

Inside the group, we expect:

- A `left` group, containing a delayed object on the left of the arithmetic operation.
  This can be either boolean, integer or float.
- A `right` group, containing a delayed object on the right of the operation.
  This can be either boolean, integer or float.
  It should have exactly the same dimensions as the `left` object.
- A `method` string scalar dataset, specifying the arithmetic method to use.
  This can be any one of `+`, `-`, `/`, `*`, `^`, `%%` (modulo) or `%/%` (integer division).
  Any HDF5 string datatype may be used here.

The type of the output object depends on the operation, the type of `left` and the type of `right`:

- For simple division, the output type is always float.
- For integer division, the output type is always integer.
- For modulo where both `left` and `right` are integer, the output type is integer.
- In all other cases, the output type is the more advanced type of `left` and `right`. 

For `left` and `right` that are of different types, the less advanced type is promoted to a more advanced type prior to applying the arithmetic operation.
If `left` and `right` are both boolean, they are first promoted to integer.
Note that no guarantees are provided with respect to the over/underflow of the output type.
