```{r, results="asis", echo=FALSE}
knitr::opts_chunk$set(error=FALSE)
if (!exists(".version")) {
    .version <- package_version("1.0")
}
```

```{r, results="asis", echo=FALSE}
cat("# Combine (", as.character(.version), ")", sep="")
```

## Overview

A combine operation involves combining one or more delayed objects along a single dimension.

## Specification

A delayed combining operation is represented as a HDF5 group with the following attributes:

- `delayed_type` should be a scalar string `"operation"`.
  Any HDF5 string datatype may be used here.
- `delayed_operation` should be a scalar string `"combine"`.
  Any HDF5 string datatype may be used here.

Inside the group, we expect:

- A `seeds` group.
  This is expected to be a [list](../_general.md#lists) of length equal to the number of seeds to be combined.
  Each seed should be a group describing a delayed object.
  All seeds should have the same dimensionality and extents, with the exception of the `along` dimension.
- An `along` scalar dataset 
```{r, results="asis", echo=FALSE}
if (.version <= package_version("1.0")) {
    cat(" of any integer datatype.")
} else {
    cat(" of any datatype that can be represented by a 64-bit unsigned integer.")
}
```
  This is a 0-based index that specifies the dimensions on which to combine objects in `seeds`.
  It should be a non-negative value that is less than the dimensionality of each object.

If all `seeds` have the same type, the output object will also be of that type.
Otherwise, the type of the output object is set to the most advanced type among all `seeds` objects.
For example, a mixture of integer and float objects will result in a float output, where all objects are promoted to float before combining them.
