```{r, results="asis", echo=FALSE}
knitr::opts_chunk$set(error=FALSE)
if (!exists(".version")) {
    .version <- package_version("1.0")
}
```

```{r, results="asis", echo=FALSE}
cat("# Constant array (", as.character(.version), ")", sep="")
```

## Overview

A constant array is an array with a constant value, typically used to store placeholder values for missingness.

## Specification

A constant array is represented as a HDF5 group with the following attributes:

- `delayed_type` should be a scalar string dataset, of any datatype that can be represented by a UTF-8 encoded string.
  It should contain the value `"array"`.
- `delayed_array` should be a scalar string dataset, of any datatype that can be represented by a UTF-8 encoded string.
  It should contain the value `"constant array"`.

Inside the group, we expect:

- A `dimensions` dataset, specifying the dimensions of the constant array.
  This should be a 1-dimensional dataset of non-zero length equal to the number of dimensions.
```{r, results="asis", echo=FALSE}
if (.version <= package_version("1.0")) {
    cat("  Any integer datatype can be used here.
  All values should be non-negative.")
} else {
    cat("  It can be of any datatype that can be represented by a 64-bit unsigned integer.")
}
```
- A `value` scalar dataset, containing the value of the constant array.
```{r, results="asis", echo=FALSE}
if (.version > package_version("1.0")) {
    cat('  This should have a `type` scalar attribute of any string datatype, which should be one of the following:
  - `"INTEGER"`, in which case `data` should have a datatype that fits into a 32-bit signed integer.
  - `"FLOAT"`, in which case `data` should have a datatype that fits into a 64-bit float.
  - `"BOOLEAN"`, in which case `data` should have a datatype that fits into a 8-bit signed integer.
  - `"STRING"`, in which case `data` should have a datatype that can be represented by a UTF-8 encoded string.')
} else {
    cat("  This can be either boolean, integer, float or string; the exact type is left to the implementation.")
}
```

```{r, results="asis", echo=FALSE}
deposit_placeholder_spiel(can.be.string=TRUE, data.name="value")
```

```{r, results="asis", echo=FALSE}
if (.version <= package_version("1.0")) {
    cat('The type of the constant array is inferred from the datatype of `value`: integer, float or string.')
} else {
    cat('The type of the constant array is set to the `type` attribute of `value`.')
}
```
