```{r, results="asis", echo=FALSE}
knitr::opts_chunk$set(error=FALSE)
if (!exists(".version")) {
    .version <- package_version("1.0")
}
```

```{r, results="asis", echo=FALSE}
cat("# Dense array (", as.character(.version), ")", sep="")
```

## Overview 

A dense array is a... dense array.

## Specification

A dense array is represented as a HDF5 group with the following attributes:

- `delayed_type` should be a scalar string `"array"`.
  Any HDF5 string datatype may be used here.
- `delayed_array` should be a scalar string `"dense array"`.
  Any HDF5 string datatype may be used here.

Inside the group, we expect:

- A `data` dataset, containing the array data.
  This should have a non-zero number of dimensions (i.e., not scalar).
```{r, results="asis", echo=FALSE}
if (.version > package_version("1.0")) {
    cat('  This should have a `delayed_type` scalar attribute of any string datatype, which should be one of the following:
  - `"integer"`, in which case `data` should have a datatype that fits into a 32-bit signed integer.
  - `"float"`, in which case `data` should have a datatype that fits into a 64-bit float.
  - `"boolean"`, in which case `data` should have a datatype that fits into a 8-bit signed integer.
  - `"string"`, in which case `data` should have a datatype that can be represented by a UTF-8 encoded string.')
} else {
    cat("  This can be either boolean, integer, float or string; the exact type is left to the implementation.")
}
```
- A `native` scalar dataset, to be interpreted as a boolean.
```{r, results="asis", echo=FALSE}
if (.version > package_version("1.0")) {
    cat('  This should have a datatype that fits into a 8-bit signed integer, where non-zero values are treated as truthy.');
} else {
    cat('  This should be of any integer datatype, where non-zero values are treated as truthy.')
}
```
  The value specifies whether the dimensions of the dense array are sorted from slowest-changing (first) to fastest-changing (last).
  If true, the dimensions of the `data` dataset are in the same order as the dimensions of the dense array.
  If false, the dimensions are saved in reverse order, i.e., the first dimension of the dense array is the last dimension of the `data` dataset.

Setting `native = 0` is frequently done for efficiency when the in-memory dense array has a different layout than the on-disk HDF5 dataset.
For example, Fortran, R and Julia use column-major order for their matrices, while C code (and HDF5) would typically use row-major order.
By setting `native = 0`, we avoid the need to reorganize the data when reading/writing from file;
however, this means that the dimensions reported by HDF5 need to be reversed to obtain the dimensions of the delayed object.

```{r, results="asis", echo=FALSE}
deposit_placeholder_spiel(can.be.string=FALSE, data.name="data")
```

The group may also contain:

- A `dimnames` group, representing a [list](../_general.md#list) of length equal to the number of dimensions in the dense array.
```{r, results="asis", echo=FALSE}
if (.version <= package_version("1.0")) {
    cat("  Each child entry corresponds to a dimension of the dense array and contains the names along that dimension.
  (Note that the ordering of `dimnames` is unrelated to the setting of `native`.
  For example, entry 0 always corresponds to the first dimension of the \"user-visible\" dense array, regardless of how it is saved in `data`;
  so if `native = 0`, entry 0 will correspond to the last dimension of `data`.)")
} else {
    cat("  Each child entry corresponds to a dimension of `data` and contains the names along that dimension, e.g., entry `0` contains names for the first dimension of `data`.")
}
```
  The absence of a child entry indicates that no names are attached to the corresponding dimension.
  Each (non-absent) entry should be a 1-dimensional string dataset of length equal to the extent of its dimension.
  Any HDF5 string datatype may be used here.

```{r, results="asis", echo=FALSE}
if (.version <= package_version("1.0")) {
    cat('The type of the constant array is inferred from the datatype of `data`: integer, float or string.
If `data` is an integer dataset, it may additionally contain an `is_boolean` attribute.
This should be an integer scalar; if non-zero, it indicates that the contents of `data` should be treated as booleans where zeros are falsey and non-zeros are truthy.')
} else {
    cat('The type of the dense array is set to the `delayed_type` attribute of `data`.')
}
```
