```{r, results="asis", echo=FALSE}
knitr::opts_chunk$set(error=FALSE)
if (!exists(".version")) {
    .version <- package_version("1.0")
}
```

```{r, results="asis", echo=FALSE}
cat("# Dimnames assignment (", as.character(.version), ")", sep="")
```

## Overview 

A dimnames assignment operation involves changing the names along one or more of the dimensions of the array.

## Specification

A delayed subsetting operation is represented as a HDF5 group with the following attributes:

- `delayed_type` should be a scalar string dataset, of any datatype that can be represented by a UTF-8 encoded string.
  It should contain the value `"operation"`.
- `delayed_operation` should be a scalar string dataset, of any datatype that can be represented by a UTF-8 encoded string.
  It should contain the value `"dimnames"`.

Inside the group, we expect:

- A `seed` group, containing a delayed object for which dimnames are to be assigned.
- A `dimnames` group, representing a [list](../_general.md#lists) of length equal to the number of dimensions in the `seed`.
  Each child entry corresponds to a dimension of `seed` and contains the names along that dimension.
  Each entry should be a 1-dimensional string dataset of length equal to the extent of its dimension.
  The datatype of each dataset should be representable by a UTF-8 encoded string.
  If a particular dataset is absent, no names are attached to the corresponding dimension.
  It is assumed that each string in each dataset is not missing.
