```{r, results="asis", echo=FALSE}
knitr::opts_chunk$set(error=FALSE)
if (!exists(".version")) {
    .version <- package_version("1.0")
}
```

```{r, results="asis", echo=FALSE}
cat("# External HDF5 array (", as.character(.version), ")", sep="")
```

## Overview

An external HDF5 array contains a reference to a HDF5 array in an external file.

## Specification

Each external array is represented as a HDF5 group with the following attributes:

- `delayed_type` should be a scalar string `"array"`.
  Any HDF5 string datatype may be used here.
- `delayed_array` should be any scalar string that starts with `"external hdf5 "` (note the space).
  Implementations are expected to add their own descriptors to define specific interprations.
  Any HDF5 string datatype may be used here.

Inside the group, we expect:

- `dimensions`, specifying the dimensions of the external array.
  This should be a 1-dimensional dataset of non-zero length equal to the number of dimensions.
  Any integer datatype can be used here.
  All values should be non-negative.
- `type`, a scalar string specifying the type.
  This should be one of `BOOLEAN`, `INTEGER`, `FLOAT` or `STRING`.
  Any HDF5 string datatype may be used here.
- `file`, a scalar string containing the path to the external HDF5 file.
  The forward slash `/` is assumed to be a file separator.
  If the `file` starts with `/`, it is assumed to be an absolute path; otherwise it should be treated as a relative path.
  Any HDF5 string datatype may be used here.
- `name`, a scalar string containing the name of the dataset or group inside `file` corresponding to the array/matrix. 
  The forward slash `/` is assumed to be a group separator.
  Any HDF5 string datatype may be used here.

This function will not check that `file` actually exists with the specified `name` entry.
The structure of the array data at `name` in the external file is also left to the implementation.
Generally, we suggest referring to HDF5 datasets for [dense arrays](../dense_array) and to HDF5 groups for [sparse matrices](../sparse_matrix).
