```{r, results="asis", echo=FALSE}
knitr::opts_chunk$set(error=FALSE)
if (!exists(".version")) {
    .version <- package_version("1.0")
}
```

```{r, results="asis", echo=FALSE}
cat("# Sparse matrix (", as.character(.version), ")", sep="")
```

## Overview 

```{r, echo=FALSE, results="asis"}
if (.version > package_version("1.0")) {
    cat("A sparse matrix is stored in the compressed sparse layout,")
} else {
    cat("A sparse matrix is stored in the compressed sparse column (CSC) layout,")
}
```
using the same notation as the [10X Genomics feature barcode matrices](https://support.10xgenomics.com/single-cell-gene-expression/software/pipelines/latest/advanced/h5_matrices).
```{r, echo=FALSE, results="asis"}
if (.version > package_version("1.0")) {
    cat("Both compressed sparse column (CSC) and compressed sparse row (CSR) matrices are supported.")
}
```

## Specification

A sparse matrix is represented as a HDF5 group with the following attributes:

- `delayed_type` should be a scalar string `"array"`.
  Any HDF5 string datatype may be used here.
- `delayed_array` should be a scalar string `"sparse matrix"`.
  Any HDF5 string datatype may be used here.

Inside the group, we expect:

- A `shape` 1-dimensional integer dataset, containing the dimensions of the matrix.
```{r, results="asis", echo=FALSE}
if (.version > package_version("1.0")) {
  cat("  The datatype should be exactly represented by a 64-bit unsigned integer.")
} else {
  cat("  The exact integer representation is left to the implementation.")
}
```
- A `data` 1-dimensional dataset, containing the values of the non-zero elements.
```{r, results="asis", echo=FALSE}
if (.version > package_version("1.0")) {
    cat('  This should have a `delayed_type` scalar attribute of any string datatype, which should be one of the following:
  - `"integer"`, in which case `data` should have a datatype that fits into a 32-bit signed integer.
  - `"float"`, in which case `data` should have a datatype that fits into a 64-bit float.
  - `"boolean"`, in which case `data` should have a datatype that fits into a 8-bit signed integer.')
} else {
    cat("  This can be integer or float; the exact datatype is left to the implementation.
  If `data` is an integer dataset, it may additionally contain an `is_boolean` attribute.
  This should be an integer scalar; if non-zero, it indicates that the contents of `data` should be treated as booleans where zeros are falsey and non-zeros are truthy.")
}
```
- An `indices` 1-dimensional dataset, 
```{r, results="asis", echo=FALSE}
if (.version > package_version("1.0")) {
    cat("  containing the row indices (CSC) or column indiecs (CSR) for the non-zero elements.
  This should have the same length as `data` and should contain integers in `[0, X)` where `X` is the number of rows (CSC) or columns (CSR) from `shape`.")
} else {
    cat("  containing the row indices for the non-zero elements.
  This should have the same length as `data` and should contain integers in `[0, X)` where `X` is the number of rows from `shape`.")
}
```
  Entries should be strictly increasing within each column, based on the ranges defined by `indptr`.
```{r, results="asis", echo=FALSE}
if (.version > package_version("1.0")) {
    cat("  The datatype should be exactly represented by a 64-bit unsigned integer.")
} else {
    cat("  The exact integer representation is left to the implementation.")
}
```
- An `indptr` 1-dimensional dataset, containing pointers into the `indices` vector.
```{r, results="asis", echo=FALSE}
if (.version > package_version("1.0")) {
    cat("  This should have length equal to `Y + 1` where `Y` is the number of columns (CSC) or rows (CSR) from `shape`.")
} else {
    cat("  This should have length equal to `Y + 1` where `Y` is the number of columns from `shape`.")
}
```
  The first element should be equal to zero and the last element should be equal to the length of `data`.
```{r, results="asis", echo=FALSE}
if (.version > package_version("1.0")) {
  cat("  The datatype should be exactly represented by a 64-bit unsigned integer.")
} else {
  cat("  The exact integer representation is left to the implementation.")
}
```
```{r, results="asis", echo=FALSE}
if (.version > package_version("1.0")) {
    cat("- A `by_column` scalar dataset, indicating whether this is a CSC matrix.
  This should have a datatype that can be exactly represented by an 8-bit signed integer.
  A non-zero value indicates that the matrix is CSC, otherwise it is treated as CSR.")
}
```

The group may also contain:

- A `dimnames` group, representing a [list](../_general.md#lists) of length 2.
  Each child entry corresponds to a dimension of `seed` and contains the names along that dimension, e.g., entry `0` contains row names.
  Missing entries indicate that no names are attached to its dimension.
  Each (non-missing) entry should be a 1-dimensional string dataset of length equal to the extent of its dimension.
  Any HDF5 string datatype may be used here.

```{r, results="asis", echo=FALSE}
deposit_placeholder_spiel(can.be.string=FALSE, data.name="data")
```

```{r, results="asis", echo=FALSE}
if (.version <= package_version("1.0")) {
    cat('The type of the sparse matrix is inferred from the datatype of `data`: integer, float or string.
Boolean matrices are identified as those with integer `data` and a truthy `is_boolean` flag.')
} else {
    cat('The type of the sparse matrix is set to the `delayed_type` attribute of `data`.')
}
```

