```{r, results="asis", echo=FALSE}
knitr::opts_chunk$set(error=FALSE)
if (!exists(".version")) {
    .version <- package_version("1.0")
}
```

```{r, results="asis", echo=FALSE}
cat("# Subset (", as.character(.version), ")", sep="")
```

## Overview

A delayed subset involves replacing a subarray of a delayed object.
If slices are applied to multiple dimensions, the subset is defined as the outer product of all slices.

## Specification

A delayed subset is represented as a HDF5 group with the following attributes:

- `delayed_type` should be a scalar string `"operation"`.
  Any HDF5 string datatype may be used here.
- `delayed_operation` should be a scalar string `"subset"`.
  Any HDF5 string datatype may be used here.

Inside the group, we expect:

- A `seed` group, containing the delayed object to be subsetted. 
  This can be of any type - boolean, integer, float or string.
- A `value` group, containing the object supplying the replacement values for subset assignment.
  This can be of any type - boolean, integer, float or string.
- An `index` group, representing a [list](../_general.md#lists) of length equal to the number of dimensions in the `seed`.
  Each child entry is named after a dimension of `seed` and contains the indices to be replaced along that dimension.
  Each entry should be a 1-dimensional integer dataset containing 0-based indices less than the extent of the corresponding dimension of `seed`;
  the length of this dataset should be equal to the extent of the corresponding dimension of `value`.
```{r, echo=FALSE, results="asis"}
if (.version > package_version("1.0")) {
  cat("  The datatype of each dataset should be exactly represented by a 64-bit unsigned integer.")
} else {
  cat("  The exact integer representation is left to the implementation.")
}
```
  The absence of an entry for a dimension indicates that the full extent of that dimension is to be replaced.

The type of the object is defined as the more advanced type of `seed` and `value`.
