```{r, results="asis", echo=FALSE}
knitr::opts_chunk$set(error=FALSE)
if (!exists(".version")) {
    .version <- package_version("1.0")
}
```

```{r, results="asis", echo=FALSE}
cat("# Unary arithmetic (", as.character(.version), ")", sep="")
```

## Overview

A unary arithmetic operation involves applying an element-wise arithmetic operation on a delayed object with a scalar or vector as the other operand,
recycling the latter across dimensions as necessary.
This is "unary" in the sense that only one delayed object is involved.

## Specification

A unary arithmetic operation is represented as a HDF5 group with the following attributes:

- `delayed_type` should be a scalar string dataset, of any datatype that can be represented by a UTF-8 encoded string.
  It should contain the value `"operation"`.
- `delayed_operation` should be a scalar string dataset, of any datatype that can be represented by a UTF-8 encoded string.
  It should contain the value `"unary arithmetic"`.

Inside the group, we expect:

- A `seed` group, containing a delayed object for which arithmetic is to be applied.
  This can be either boolean, integer or float.
  Booleans are promoted to integers for the purpose of this operation.
- A `method` string scalar dataset, specifying the arithmetic method to use.
  This can be any one of `+`, `-`, `/`, `*`, `^`, `%%` (modulo) or `%/%` (integer division).
  The datatype of the dataset should be representable by a UTF-8 encoded string.
- A `side` string scalar dataset, describing the side of the `seed` object to apply the operation.
  This can be `"left"`, when `value` is applied to the left of `seed`, e.g., `value - seed`;
  or `"right"`, when `value` is applied to the right of `seed`, e.g., `seed - value`.
  For `+` and `-` as pure unary methods, this may also be `"none"`.
  The datatype of the dataset should be representable by a UTF-8 encoded string.

For `side != "none"`, we also expect:

- A `value` dataset, which may be either scalar or 1-dimensional.
```{r, echo=FALSE, results="asis"}
if (.version > package_version("1.0")) {
    cat('  This should have a `type` scalar attribute of any string datatype, which should be one of the following:
  - `"INTEGER"`, in which case `data` should have a datatype that fits into a 32-bit signed integer.
  - `"FLOAT"`, in which case `data` should have a datatype that fits into a 64-bit float.
  - `"BOOLEAN"`, in which case `data` should have a datatype that fits into a 8-bit signed integer.
    Booleans are promoted to integers for the purpose of this operation.')
} else {
    cat("  This can be either integer or float; the exact type is left to the implementation.")
}
```

If `value` is 1-dimensional, we also expect:

- An `along` scalar integer dataset, specifying the dimension on which to apply the operation with `value`.
```{r, echo=FALSE, results="asis"}
if (.version <= package_version("1.0")) {
    cat("  The exact integer representation is left to the implementation.")
} else {
    cat("  This dataset should have a datatype that fits into a 64-bit unsigned integer.")
}
```
  The length of `value` should be equal to the extent of the dimension specified in `along`.

```{r, results="asis", echo=FALSE}
deposit_placeholder_spiel(can.be.string=FALSE, data.nam="value")
```

The type of the output object depends on the operation, the type of `seed` and the type of `value`:

- For simple division, the output type is always float.
- For integer division, the output type is always integer.
- For all other operations:
  - If the types of `seed` and `value` are the same, the output type of the arithmetic operation is equal to that type.
  - Otherwise, the less advanced type is promoted to a more advanced type, and the output type of the arithmetic operation is equal to the promoted type.

Note that no guarantees are provided with respect to the over/underflow of the output type.
