```{r, results="asis", echo=FALSE}
knitr::opts_chunk$set(error=FALSE)
if (!exists(".version")) {
    .version <- package_version("1.0")
}
```

```{r, results="asis", echo=FALSE}
cat("# Unary comparison (", as.character(.version), ")", sep="")
```

## Overview

A unary comparison involves applying an element-wise comparison on a delayed object with a scalar or vector as the other operand,
recycling the latter across dimensions as necessary.
This is "unary" in the sense that only one delayed object is involved.

## Specification

A unary comparison is represented as a HDF5 group with the following attributes:

- `delayed_type` should be a scalar string `"operation"`.
  Any HDF5 string datatype may be used here.
- `delayed_operation` should be a scalar string `"unary comparison"`.
  Any HDF5 string datatype may be used here.

Inside the group, we expect:

- A `seed` group, containing a delayed object for which comparison is to be applied.
  This can be either boolean, integer, float, or string.
- A `method` string scalar dataset, specifying the comparison method to use.
  This can be any one of `==`, `<`, `>`, `>=`, `<=`, or `!=`. 
  Any HDF5 string datatype may be used here.
- A `side` string scalar dataset, describing the side of the `seed` object to apply the operation.
  This can be `"left"`, when `value` is applied to the left of `seed`, e.g., `value > seed`;
  or `"right"`, when `value` is applied to the right of `seed`, e.g., `seed > value`.
  Any HDF5 string datatype may be used here.
- A `value` dataset, which may be either scalar or 1-dimensional.
```{r, echo=FALSE, results="asis"}
if (.version > package_version("1.0")) {
    cat('  This should have a `delayed_type` scalar attribute of any string datatype, which should be one of the following:
  - `"integer"`, in which case `data` should have a datatype that fits into a 32-bit signed integer.
  - `"float"`, in which case `data` should have a datatype that fits into a 64-bit float.
  - `"boolean"`, in which case `data` should have a datatype that fits into a 8-bit signed integer.
  - `"string"`, in which case `data` should have a datatype that can be represented by a UTF-8 encoded string.
    This should only be used when `seed` is also a string type.')
} else {
    cat('  If `seed` contains strings, so should `value`; otherwise, both `seed` and `value` should be any of boolean, integer or float.
  The exact type representation is left to the implementation.')
}
```

If `value` is 1-dimensional, we also expect:

- An `along` integer scalar dataset, specifying the dimension on which to apply the operation with `value`.
```{r, echo=FALSE, results="asis"}
if (.version <= package_version("1.0")) {
    cat("  The exact integer representation is left to the implementation.")
} else {
    cat("  This dataset should have a datatype that fits into a 64-bit unsigned integer.")
}
```
  The length of `value` should be equal to the extent of the dimension specified in `along`.

```{r, results="asis", echo=FALSE}
deposit_placeholder_spiel(can.be.string=FALSE, data.nam="value")
```

The type of the output object is always boolean.
For `left` and `right` that are of different types, the less advanced type is promoted to a more advanced type prior to performing the comparison.

